Supporting Information for ``Robust Adaptation to Multi-Scale Climate Variability''

### 2019-04-08 report-earths-future/si_template_2019.tex
add line to caption noting colorbar nonlinearity
Final version with manu suggestion

@@

\begin{figure}
      \includegraphics[width=\textwidth]{enso_wavelet.png}
      \caption{
        Wavelet analysis of the synthetic annual NINO3 time series described in Section 2.1.
        (L): wavelet power spectrum.
        (R): global (average) power spectrum.
        Blue dots indicate frequencies which are significant at $\alpha=0.10$ and red dots frequencies which are significant at $\alpha=0.05$ compared to white noise.
      }\label{fig:enso-ts}
    \end{figure}

>>>>

\subsection{Implications of Bias and Variance}

Figure \ref{fig:conceptual-bias-variance} shows a schematic representation of the implications of too-low or too-high bias and variance in climate risk projections.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Bias-Variance-Sketch.pdf}
  \caption{
    Consequences of model bias or incorrect model representation of uncertainty.
    If an estimate has a positive bias and overestimates uncertainty, the instrument may be too expensive.
    If an estimate has negative bias and underestimates uncertainty, it will be likely to fail.
  }\label{fig:conceptual-bias-variance}
\end{figure}

\begin{figure}
      \includegraphics[width=\textwidth]{enso_wavelet.png}
      \caption{
        Wavelet analysis of the synthetic annual NINO3 time series described in Section 2.1.
        (L): wavelet power spectrum.
        Note that the color bar uses a quantile scale and is thus nonlinear.
        (R): global (average) power spectrum.
        Blue dots indicate frequencies which are significant at $\alpha=0.10$ and red dots frequencies which are significant at $\alpha=0.05$ compared to white noise.
      }\label{fig:enso-ts}
    \end{figure}
